Surface programmable materials

### 2024-08-26 paper/main.tex
update

\newcommand{\jgl}[1]{[{\color{green}{JGL: #1}}]}
\newcommand{\s}{\mathbf {s}}
\newcommand{\net}[1]{{\textsc{#1}}}
\newcommand{\argmin}{\mathop{\mathrm{argmin}}\limits}
\newcommand{\Eq}[1]{Eq.~(\ref{#1})}
\newcommand{\Fig}[1]{Fig.~\ref{#1}}

@@

@@

Let us define a model Hamiltonian on a 2D lattice as
\begin{equation}\label{eq:toy-hamiltonian}
H = \sum_{\text{each gadget}} (n_{i+1, t} \land \neg(n_{i, t} \land \neg n_{i-1, t})) \veebar n_{i,t+1},
\end{equation}
where $n_{i, t} \in \{0, 1\}$ is the state of the cell at row $i$ and column $t$.
Its ground state with energy $0$ encodes a $110$ cellular automaton, where the direction of computation is from the left to right.

>>>>

\newcommand{\jgl}[1]{[{\color{blue}{JGL: #1}}]}
\newcommand{\s}{\mathbf {s}}
\newcommand{\net}[1]{{\textsc{#1}}}
\newcommand{\argmin}{\mathop{\mathrm{argmin}}\limits}
\newcommand{\Eq}[1]{Eq.~(\ref{#1})}
\newcommand{\Fig}[1]{Fig.~\ref{#1}}

@@

\jgl{Please cover the following topics: \begin{enumerate}
    \item Computational models driven by the thermodynamics (cooling, or lowering the free energy), i.e. Brownian machine, such as DNA and Ising machine.
    \item Potential advantages: energy saving, parallelism, no size limits (robust to quantum effects). Disadvantages: slow, error-prone.
    \item Two approaches to lower the free energy: entropy driven, or energy based modeling. Embedding a computational model to energy models, the non-deterministic version: Circuit SAT, QUBO, Spin-Glass and Ising machine.
    \item Crutial issue of energy based model, hard to thermalize, hard to prepare.
    \item Crystal based computing: Cellular automata as a computational model.
    \item The method to thermalize, inspired from crystalization and heat zone.
\end{enumerate}
}

@@

Let us define a model Hamiltonian on a 2D lattice of size $S \times T$ as
\begin{equation}\label{eq:toy-hamiltonian}
H = \sum_{t=1}^{T-1}\sum_{i=1}^{S} (n_{i+1, t} \land \neg(n_{i, t} \land \neg n_{i-1, t})) \veebar n_{i,t+1},
\end{equation}
where $n_{i, t} \in \{0, 1\}$ is the state of the cell at row $i$ and column $t$, the boundary is periodic in the space direction, i.e. $n_{0, t} = n_{S, t}$.
Its ground state with energy $0$ encodes a $110$ cellular automaton, where the direction of computation is from the left to right.
